%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,9pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\hypersetup{
	hidelinks=true,
	urlcolor = [rgb]{0,0,0.5}
}
\usepackage{fancyhdr}

\usepackage{tgheros}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\definecolor{blue}{rgb}{0.08, 0.3, 0.75}
% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\color{blue}\bfseries\scshape\raggedright\large
}{}{0em}{}[\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item[]\small{
    \textbf{#1}{: #2 }% \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-2pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt]}
\newcommand{\resumeSubHeadingListStartNM}{\begin{itemize}[noitemsep, leftmargin=12pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[noitemsep, leftmargin=8pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\fontfamily{qhv}\selectfont
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \href{http://tiny.cc/rkrsnGScholar}{\textbf{{\color{blue} \LARGE \textsc{Rahul} KRISHNA}}} 
  & Email : 
  \href{mailto:rkrish11@ncsu.edu}{rkrish11@ncsu.edu}\\
  \href{http://rkrsn.us/}{http://rkrsn.us} $\diamond$ 
  Github: \href{https://github.com/rahlk}{github.com/rahlk} & Mobile : 
  +1-919-396-4143 \\
  119 Karen Ct, Cary, NC 27511& LinkedIn: 
  \href{https://www.linkedin.com/in/rkrsn/}{linkedin.com/in/rkrsn}\\[-0.3cm]
\end{tabular*}
\vspace{0.2em}

% %-----------Objective-----------------
% \section{Objective}
% Now that  DevOps  is done, it is time to solve our next grand challenge; i.e. how to integrate  AI + SE methods so human and artificial intelligence  can better understand and help each other to solve 21st century business problems
% \vspace{-0.5em}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {PhD in Computer Science}{Jun. 2015 -- Dec. 2018 (expected)}
      {North Carolina State University}{Raleigh, NC}\vspace{-1pt}
  \resumeSubheading
      {MS in Electrical Engineering}{Aug. 2013 -- May 2015}
      {North Carolina State University}{Raleigh, NC}\vspace{-1pt}
    \resumeSubheading
      {BE in Electronics \& Communication}{Aug. 2009 -- May 2013}
      {Ramaiah Institute Of Technology}{Bengaluru, India}\vspace{-0.2cm}
        \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{General Expertise}{Statistics, Machine 
    Learning, Natural Language Processing, Program Analysis, Optimization;}\\[-0.6em]
    \resumeSubItem{Programming}{Proficient: Python (5+ years), MATLAB (4+ years), C/C++ (2+ years). Working Knowledge: R, Javascript, Scala;}
    % \resumeSubItem{DevOps}{Ansible, Vagrant, Travis, Jenkins, Docker.}
  \resumeSubHeadingListEnd

\section{Work Experience}

\resumeSubHeadingListStart

\resumeSubheading{Phase Change LLC}{Golden, CO}
{Research intern, Financial Data Mining}{June 2018 - Aug. 2018}
\resumeItemListStart
\item Developed an ontology based vector embedding model to automatically extract financial domain knowledge from COBOL.
\item Achieved confidence scores $\geq$80\% on determining banking concepts in COBOL code as measured by surveying subject matter experts and active COBOL developers. 
\item[]\textit{\textbf{Languages:} Python; \textbf{Frameworks:} Apache Jena, Gensim; \textbf{Skills:} Static Code Analysis, Ontology development, SPARQL.}
\resumeItemListEnd

\resumeSubheading{LexisNexis Legal \& Professional}{Raleigh, NC}{Data Science Intern, Natural Language Processing and Information Retrieval}{May 2017 - Aug 2017}
\resumeItemListStart
\item Developed and deployed a text summarization framework for generating ``headnotes'' in more than 1 Million legal documents. 
\item Designed a scalable clustering and a classification scheme with \textit{doc2vec} to categorize documents into specific legal topics; 
\item Demonstrated that the above framework can reduce document review time by $\geq$50\% according to in-house user surveys.
\item[]\textit{\textbf{Languages:} Python, Scala; \textbf{Frameworks:} Tensorflow, Spark, Livy, AWS--EMR, Lambda, CloudFormation; \textbf{Skills:} ML, NLP.}
\resumeItemListEnd

\resumeSubheading{LexisNexis Legal \& Professional}{Raleigh, NC}{Data Science Intern, Natural Language Processing and E-Discovery}{May 2016 - Aug 2016}
\resumeItemListStart
\item Designed a sandbox application for automated document retrieval in Technology Assisted Review (TAR) and E-Discovery. 
\item Improved the classification accuracy of SVM in highly skewed samples by $\approx$ 20\% using active reinforcement learning.
\item[]\textit{\textbf{Languages:} Python, Javascript; \textbf{Frameworks:} Spark, Elasticsearch, Logstash, Flask; \textbf{Skills:} ML, NLP, Web design.}

\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Research Projects}

\resumeSubHeadingListStart

\resumeSubheading{Planning in Software Engineering}{Raleigh, NC}
{NSF funded project in the RAISE Lab}{Sept 2015 - Present}
\resumeItemListStart
	\item Developed a novel planning algorithm called XTREE to assist 
	developers in software maintenance and defect reduction.
	\item Demonstrated that XTREE can generate succinct plans (75\% smaller plans than other approaches). 
	\item Demonstrated that XTREE can reduce defects by more than 80\% in several cases.
\resumeItemListEnd

\resumeSubheading{Transfer Learning in Software Engineering}{Raleigh, NC}{NSF funded project in the RAISE Lab}{Sept 2015 - 
Present}
\resumeItemListStart
	\item Demonstrated the existence of a \textit{``Bellwether Effect''} in 
	several domains within software engineering. 
	\item Demonstrated that the \textit{bellwether} projects outperformed state-of-the-art transfer learners with Recall and False Alarm $\geq75\%$.
\resumeItemListEnd

\resumeSubheading{IBM Software Group~\textnormal{(Research~Collaboration)}}{Research Triangle Park, NC}{Assessing Development Practices in opensource and in-house projects.}{March 2017 - 
May 2018}
\resumeItemListStart
	\item Developed time-series models to forecast issues, bugs, and enhancements in 800+ opensource \& IBM in-house projects.
	\item Demonstrated effectiveness of moving-window ARIMA models in forecasting 4-weeks of future issues, bugs, and enhancements in 66\% of the projects with an accuracy of 85-95\% (IBM in-house) and 75-85\% (opensource). 
	\item Studied the effect of CI/CD and developer collaboration in reducing bugs in 800+ opensource \& IBM in-house projects.
	\item Demonstrated that earlier adoption of CI/CD stimulates developer collaboration and reduces bugs in IBM in-house projects.
\resumeItemListEnd

\resumeSubheading{LexisNexis Legal \& Professional~\textnormal{(Research~Collaboration)}}{Raleigh, NC}{Software Engineering for Big Data and Industrial Text Mining}{Sept 2015 - May 2017}
%{\footnotesize \textit{(Research %collaboration)}}
\resumeItemListStart
\item Validated large scale natural language processing pipelines empirically
for technology assisted review at LexisNexis.
\item Developed a quantitative 6-point metric set for assessing best-practices in industrial text mining.
\item Demonstrated the effectiveness of the 6-point metric in alleviating effort in making design choices for industrial text mining.
\resumeItemListEnd


\resumeSubHeadingListEnd

\section{Teaching Assistantships}

\resumeSubHeadingListStart
\resumeSubheading{CSC591: Foundations of Software Science}{Fall 2018 (ongoing)}{Special Topics in Computer Science}{}
\resumeItemListStart
	\item Assisting in teaching the foundations of software engineering principles to a class of 30 graduate students.
	\item Offering guest lectures on intermediate and advanced functional programming in python with a focus on best practices.
	\item Assisting in designing and grading homework assignments and mid-semester examinations.
\resumeItemListEnd
\resumeSubheading{CSC591: Automated Software Engineering}{Fall 2016}{Special Topics in Computer Science}{}
\resumeItemListStart
	\item Aided in teaching the principles of software engineering and applied data science to a class of 49 graduate students.
	\item Assisted in designing and grading homework assignments, mid-semester examinations, and final project reports.
	\item Offered guest lectures on the state-of-the-art in software engineering, software testing, and maintainability research.
	\item Assisted in mentoring over 12 distinct class projects on applying data mining, metaheuristic search, and natural language processing to software engineering.
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Selected Publications}
\begin{enumerate}[label={[\arabic*]}, leftmargin=15pt]

    \item\small \underline{Krishna, R.} \& Menzies, T.. \textit{``Bellwethers:
    A Baseline Method For Transfer Learning''}. In \textbf{IEEE Transactions on Software Engineering, 2018}. Online: 
    \href{https://arxiv.org/abs/1703.06218}{https://arxiv.org/abs/1703.06218}\vspace{-6pt};

    \item\small \underline{Krishna, R.}, Menzies, T., \& Layman, L. 
    \textit{``Less is more: Minimizing code reorganization using XTREE''}. In 
    \textbf{Information and Software Technology, 2017}. 
    Online:  
    \href{https://arxiv.org/abs/1609.03614}{https://arxiv.org/abs/1609.03614}\vspace{-6pt};
    
    \item\small  \underline{Krishna, R.}, Menzies, T., \& Fu, W. \textit{``Too
    much automation? The Bellwether Effect and its Implications for Transfer 
    Learning.''} In \textbf{Intl. Conference on Automated Software 
    Engineering, 2016}. Online: 
    \href{https://doi.org/10.1145/2970276.2970339}{https://doi.org/10.1145/2970276.2970339}\vspace{-6pt};
    
    \item\small \underline{Krishna, R.}, Agrawal, A., Rahman, A., Sobran, A., 
    \& Menzies, T. \textit{``What is the Connection Between Issues, Bugs, and 
    Enhancements? (Lessons Learned from 800+ Software Projects)''}. 
    \textbf{Intl. Conf. Software Engineering, 2018 SEIP}. Online: 
    \href{https://arxiv.org/abs/1710.08736}{https://arxiv.org/abs/1710.08736}\vspace{-6pt};
    
    \item\small \underline{Krishna, R.}, Yu, Z., Agrawal, A., Dominguez, M., Wolf, D. \textit{``The `BigSE' Project: Lessons Learned from Validating Industrial Text Mining. ''}. In \textbf{Intl. Workshop on Big Data Software Engineering (BIGDSE), 2016}. Online: \href{http://tiny.cc/BIGDSE16}{http://tiny.cc/BIGDSE16}\vspace{-6pt};

    \item\small \underline{Krishna, R.} \& Menzies, T. \textit{``Actionable=Cluster+Contrast?''}. In \textbf{Intl. Conference on Automated Software Engineering Workshop, 2015}. Online:~\href{http://tiny.cc/ase15action}{http://tiny.cc/ase15action}\vspace{-6pt};
    
    \item\small Ganesh, M.R., \underline{Krishna, R.}, Manikantan, K. \& Ramachandran, S., \textit{``Entropy based Binary Particle Swarm Optimization and classification for ear detection''}. In \textbf{Engineering Applications of Artificial Intelligence, 2014.}, Online:~\href{http://tiny.cc/EBPSO14}{http://tiny.cc/EBPSO14}\vspace{-6pt};
    
    \item\small Chen, J., Nair, V., \underline{Krishna, R.}, \& Menzies, T. 
    \textit{``Sampling as a Baseline Optimizer for Search-based Software 
    Engineering''}. In \textbf{IEEE Transactions on Software Engineering, 2018}. Online: 
    \href{https://arxiv.org/abs/1608.07617}{arXiv:1608.07617}\vspace{-6pt};
    
    \item\small Chen, D., Fu, W., \underline{Krishna, R.}, \& Menzies, T. \textit{``Applications of psychological science for actionable analytics''}. In \textbf{Intl. Conference on Foundations of Software Engineering, 2018}. Online: 
    \href{https://arxiv.org/abs/1803.05067}{arXiv:1803.05067}\vspace{-6pt};
    
    \item\small Agrawal, A.,  Rahman, A., \underline{Krishna, R.}, Sobran, A.
    \& Menzies, T. \textit{``We Don't Need Another Hero? The Impact of `Heroes' on Software Development''}. 
    \textbf{Intl. Conf. Software Engineering, 2018 SEIP}. Online: 
    \href{https://arxiv.org/abs/1710.09055}{arXiv:1710.09055}\vspace{-6pt};
    
    \item\small Rahman, A., Agrawal, A., \underline{Krishna, R.}, Sobran, A.
    \& Menzies, T. \textit{``Characterizing The Influence of Continuous Integration. Empirical Results from 250+ Open Source and Proprietary Project''}. 
    \textbf{Intl. Conference on Foundations of Software Engineering, SWAN 2018}. Prerint: 
    \href{https://arxiv.org/pdf/1711.03933}{https://arxiv.org/pdf/1711.03933}\vspace{-6pt};
    
    
\end{enumerate}

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
